Multi-target detection with application to cryo-electron microscopy

### 2019-02-27 inverse_problems/inverse_problems.tex
no message

A signal is determined uniquely by its second- and third-order autocorrelations. Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
%
\begin{equation}
%
z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
\label{eq-uniqueness}
%
\end{equation}
This proves the following useful fact:
\begin{proposition} \label{prop:uniqueness}
	%
	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$. \TODO{Definitely only clear for the homogeneous case}
\end{proposition}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{KLXP/XP1}
	\caption{In the $N \to \infty$ regime (access to exact moments, excluding biased entries) and with known uniform densities, it seems $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments. CPU time in seconds. Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed moments. Similar to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
	\label{fig:KLXP}
\end{figure}

>>>>

A signal is determined uniquely by its second- and third-order autocorrelations. Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
%
\begin{equation}
%
z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
\label{eq-uniqueness}
%
\end{equation}
This proves the following useful fact:
\begin{proposition} \label{prop:uniqueness}
	%
	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$. 
\end{proposition}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{KLXP/XP1}
	\caption{In the $N \to \infty$ regime (access to exact autocorrelations, excluding biased entries) and with known uniform densities, it seems $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments. CPU time in seconds. Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed moments. Similar to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
	\label{fig:KLXP}
\end{figure}
